Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-13 rainbowCAM.tex
some typos are corrected, update of legende in plots 6-7 and some reformulated paragraphs, please find remarks in pdf

CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios. In 1994, Andersson and Thylwe \cite{Andersson:1994rk} described the scattering of scalar waves by a Schwarzschild BH by utilising CAM techniques, and they showed that, in this case, Regge poles are associated with ``surface waves'' localised near the unstable light ring at $r=3M$ (later it was shown that the corresponding quasinormal modes are Breit-Wigner type resonances generated by these surface waves \cite{Decanini:2002ha}). Recently, Folacci and Ould Elhadj have shown that CAM methods can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields \cite{Folacci:2019cmc} and gravitational waves \cite{Folacci:2019vtt} on the Schwarzschild spacetime. Moreover, they have obtained an approximate  formula (see Sec.~IV in Ref.~\cite{Folacci:2019vtt}) that accurately describes both the `orbiting' and `glory' oscillations in black hole scattering cross sections in the short-wavelength regime. This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue \sam{Mohamed, please correct this if wrong.}. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles \cite{Decanini:2011xi, Decanini:2011xw}.

>>>>

%CAM theory, originally developed for high-energy physics applications, has been successfully applied to black hole scattering scenarios. In 1994, Andersson and Thylwe \cite{Andersson:1994rk} described the scattering of scalar waves by a Schwarzschild BH by utilising CAM techniques, and they showed that, in this case, Regge poles are associated with ``surface waves'' localised near the unstable light ring at $r=3M$ (later it was shown that the corresponding quasinormal modes are Breit-Wigner type resonances generated by these surface waves \cite{Decanini:2002ha}). Recently, Folacci and Ould Elhadj have shown that CAM methods can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields \cite{Folacci:2019cmc} and gravitational waves \cite{Folacci:2019vtt} on the Schwarzschild spacetime. Moreover, they have obtained an approximate  formula (see Sec.~IV in Ref.~\cite{Folacci:2019vtt}) that accurately describes both the `orbiting' and `glory' oscillations in black hole scattering cross sections in the short-wavelength regime. This approximation arises from applying WKB theory to characterise the Regge pole with the smallest imaginary part, and its residue \sam{Mohamed, please correct this if wrong.}. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles \cite{Decanini:2011xi, Decanini:2011xw}.

 \moh{Remark to Tom and Sam : I reformulated the following paragraph! What do you think}\\

The CAM theory originally developed to deal  theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld ~\cite{Sommerfeld49}) has since been  extensively used in several domains of physics involving resonant scattering theory (see,\textit{e.g.}, Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nus92,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics). And since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios. They, in particular, described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, also showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere). Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and using the concept of Regge trajectories, they have been able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}. Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time. Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}. Also, was obtained an alternative description of gravitational radiation from black holes based on CAM theory~\cite{Folacci:2018sef}.
